### 2020-04-29 README.rmd
Updated README.

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the pres_list elements.

# Output an html document to a string.
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(pres_list, ld))

doc
```

@@

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2",                     # The packges needed to render plots.
               decorator = list(ggplot = identity))     # What to do with the plot types.

# Output an html document to a string.
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                      author = "Francis Anscombe",
                      date = "1973"),
  ld_make_chunks(ld))

doc
```

>>>>

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2"))                    # The packges needed to render plots.

# Output an html document to a string.
doc <- c(
  as.character(
    ld_rmarkdown_header("Anscombe's Quartet",
                        author = "Francis Anscombe",
                        date = "1973")),
  ld_make_chunks(ld))

cat(paste(doc, collapse = "\n"))
```

@@

# Create a listdown object.
ld <- listdown(load_cc_expr = readRDS("pres-list.rds"), # The expression to load pres_list.
               package = "ggplot2")                     # The packges needed to render plots.

# Output an html document to a string.
doc <- c(
  as.character(
    ld_rmarkdown_header("Anscombe's Quartet",
                        author = "Francis Anscombe",
                        date = "1973")),
  ld_make_chunks(ld))

cat(paste(doc, collapse = "\n"))
```
